---
title: "Reproduction and robustness checks based on OSF_Analyses.R script"
date: last-modified
freeze: true
cache: true
format:
  html:
    embed-resources: true
    number-sections: true
    toc: true
---

## Set-up

Load packages and set custom functions as listed in original script:

```{r}
#| label: original code lines 1-36

#####
# load packages
library(dplyr)
library(readr)
set.seed(999)
library(scales)
library(bootstrap)
library(knitr)
library(papeR)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
library(compute.es)
library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(ggplot2)
library(reshape2)
library(rjson)
library(jsonlite)
library(Matrix)
library(lme4)
library(psych)
library(lmtest)
library(sjPlot)
library(wesanderson)
library(cowplot)
library(magick)
library(ggrepel)

# From Mike Frank
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)} #  mean(x,na.rm=na.rm) -
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) } #-

```

Load additional packages needed for our reproduction and robustness checks:

```{r}
library(here)
```

## Data import

### Read in and process English data from Studies 1 thru 3

```{r}
#| label: adaptation of code lines 40-74 to include {here} paths

#import and merge all three CSV files into one data frame
data <- list.files(path = here("R_scripts", "scripts_and_data_original", "Data_Analysis_original"),  # Identify all CSV files
                   pattern = "*english.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%  # Store all files in list
  bind_rows        # Combine data sets into one data set 


data = data %>%
  dplyr::mutate(TrialType = ifelse(left_gender == right_gender, 
                                   "RaceTrial","GenderTrial"),
                GenderTrialType = ifelse(left_race ==  "black" & right_race == "black",
                                         "BlackTrial","WhiteTrial"),
                RaceTrialType = ifelse(left_gender == "woman" & right_gender == "woman", 
                                       "WomanTrial", "ManTrial")) 


#Create column for "Like Me" (i.e. if ppts mentioned the person most like them first, or second)

data$Like_Me_Gender <- ifelse(data$first_person_gender == data$ppt_gender, 1, 0) #create numerical column
data$Like_Me_Race <- ifelse(data$first_person_race == data$ppt_race, 1, 0) #create numerical column
data$OverallLikeMe = ifelse(data$TrialType == "RaceTrial", data$Like_Me_Race, data$Like_Me_Gender)

# Set coding for contrasts

data$syntax = as.factor(data$syntax)
contrasts(data$syntax)[1] = -1

data$ppt_race = as.factor(data$ppt_race)
contrasts(data$ppt_race)[1] = -1

data$ppt_gender = as.factor(data$ppt_gender)
contrasts(data$ppt_gender)[1] = -1
```

### Import and process data from intuitions study

```{r}
#| label: reproduction of code lines 77-84 to include {here} paths

intuitions_original = read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "rating_study.csv")) %>%
  select(-...1)

intuitions_passive = read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "rating_study_passive.csv")) %>%
  mutate(ppt_age = NA, responses_new_reversed = NA)

intuitions = rbind(intuitions_original, intuitions_passive)

```

The script imports the file `empathy_study_data.csv`, which is not result of the corresponding preprocessing script (osfstorage-archive/Data Preprocessing/EmpathyStudy/process_data.R):

```{r}

#| label: reproduction of code lines 87-94 to include {here} path

#####
# Import and process empathy data

empathy_data = read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "empathy_study_data.csv")) %>%
  filter(condition != "catch")  %>%
  mutate(verb = gsub("_conjoined","",verb),
         verb = gsub("_active","",verb),
         verb = gsub("_passive","",verb))

```

### Import Chinese data

```{r}
#| label: reproduction code lines 98-106 to include {here} paths

chinese_data = read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "study4_chinese.csv"))

# the here() function enables us to write relative paths

chinese_data$ppt_gender = as.factor(chinese_data$ppt_gender)
contrasts(chinese_data$ppt_gender)[1] <- -1
chinese_data$condition = as.factor(chinese_data$condition)
contrasts(chinese_data$condition)[1] <- -1
```

## Data combining and processing

### Combine and process data from studies 1-3 with Chinese data

```{r}
#| label: reproduction of code lines 109-123 to include {here} paths

data_for_groups = bind_rows(data, read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "data5_chinese.csv")) %>% mutate(study = "study5")) # data5_chinese is just a subset of the columns in study4_chinese.csv

data_for_groups = data_for_groups %>% 
  mutate(TrialType = ordered(ifelse(TrialType %in% c("RaceTrial","Race Trials"), "Race Trials","Gender Trials"), levels = c("Race Trials","Gender Trials")))

data_for_groups$ppt_gender = as.character(data_for_groups$ppt_gender)
data_for_groups[data_for_groups$ppt_demog == "Asian Man",]$ppt_gender = "man"
data_for_groups[data_for_groups$ppt_demog == "Asian Woman",]$ppt_gender = "woman"

data_for_groups$ppt_race = as.character(data_for_groups$ppt_race)
data_for_groups[data_for_groups$ppt_demog == "Asian Man",]$ppt_race = "asian"
data_for_groups[data_for_groups$ppt_demog == "Asian Woman",]$ppt_race = "asian"

data_for_groups$ppt_race = factor(data_for_groups$ppt_race, levels = c("white","black","asian"))
data_for_groups$ppt_gender = factor(data_for_groups$ppt_gender, levels = c("man","woman"))

```

## Data processing for graphs

### Code for making the graphs for studies 1-3

```{r}
#| label: original code lines 132-180

data$syntax_labels = ifelse(data$syntax == "transitive","Transitive",
                            ifelse(data$syntax == "conjoined","Intransitive",ifelse(
                              data$syntax == "active","Active","Passive"
                            )))

like_me_averages_subj <- data %>%
  dplyr::mutate(OverallLikeMe2 = OverallLikeMe) %>%
  dplyr::group_by(subject,TrialType,syntax_labels,study) %>%
  dplyr::summarise(OverallLikeMe.m = 100*mean(OverallLikeMe2))

like_me_averages_summary <- data %>%
  dplyr::group_by(subject,TrialType,syntax_labels,study) %>%
  dplyr::summarise(OverallLikeMe.m = 100*mean(OverallLikeMe))%>%
  dplyr::group_by(TrialType,syntax_labels,study) %>%
  dplyr::summarise(OverallLikeMe.mean = mean(OverallLikeMe.m),
                   OverallLikeMe.sd = sd(OverallLikeMe.m),
                   OverallLikeMe.se = sd(OverallLikeMe.m)/sqrt(length(subject)),
                   OverallLikeMe.high = ci.high(OverallLikeMe.m),
                   OverallLikeMe.low = ci.low(OverallLikeMe.m))


study1_graph <- ggplot(subset(like_me_averages_summary, study == "study1"), 
                       aes(x = syntax_labels,y = OverallLikeMe.mean,fill = syntax_labels)) +
  #geom_path()+
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_jitter(data = subset(like_me_averages_subj, study == "study1"), aes(y = OverallLikeMe.m),alpha = 0.03, size = 1,
              position = position_jitter(width=0.1,height=0)) +
  geom_linerange(color = "black",data = subset(like_me_averages_summary, study == "study1"),aes(ymax = OverallLikeMe.high, ymin =
                                                                                                  OverallLikeMe.low)) +
  geom_point(size = 2.5, pch = 21,  color = "black",stroke = 0.7) +
  labs(fill = "Participant Gender") +
  theme_cowplot()+
  theme(legend.position="none", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  ylab("") +
  xlab("") +
  ylim(c(20,80)) +
  geom_hline(yintercept = 50, size =0.5, linetype = 2)+
  facet_wrap(~TrialType, labeller = as_labeller(c(GenderTrial='Gender Trials', RaceTrial='Race Trials')))+
  coord_flip()+
  guides(colour="none")#+
# scale_y_continuous(breaks=c(5,25,40,50,60,75,95),
#                    trans = squish_trans(c(40, 60))) 

study1_graph

study2_graph <- ggplot(subset(like_me_averages_summary, study == "study2"), 
                       aes(x = syntax_labels,y = OverallLikeMe.mean,fill = syntax_labels)) +
  #geom_path()+
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_jitter(data = subset(like_me_averages_subj, study == "study2"), aes(y = OverallLikeMe.m),alpha = 0.03, size = 1,
              position = position_jitter(width=0.1,height=0)) +
  geom_linerange(color = "black",data = subset(like_me_averages_summary, study == "study2"),aes(ymax = OverallLikeMe.high, ymin =
                                                                                                  OverallLikeMe.low)) +
  geom_point(size = 2.5, pch = 21,  color = "black",stroke = 0.7) +
  labs(fill = "Participant Gender") +
  theme_cowplot()+
  theme(legend.position="none", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  ylab("") +
  xlab("") +
  ylim(c(20,80)) +
  geom_hline(yintercept = 50, size =0.5, linetype = 2)+
  facet_wrap(~TrialType, labeller = as_labeller(c(GenderTrial='Gender Trials', RaceTrial='Race Trials')))+
  coord_flip()+
  guides(colour="none")+
  #scale_y_continuous(breaks=c(5,25,40,50,60,75,95),
  #                   trans = squish_trans(c(40, 60))) +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

study2_graph

study4_graph <- ggplot(subset(like_me_averages_summary, study == "study4"), aes(x = syntax_labels,y = OverallLikeMe.mean,fill = syntax_labels)) +
  #geom_path()+
  scale_color_hue(h = c(200,270))+
  scale_fill_hue(h = c(200,270))+
  geom_jitter(data = subset(like_me_averages_subj, study == "study4"), aes(y = OverallLikeMe.m),alpha = 0.05, size = 1,
              position = position_jitter(width=0.1,height=0)) +
  geom_linerange(color = "black",data = subset(like_me_averages_summary, study == "study4"),aes(ymax = OverallLikeMe.high, ymin =
                                                                                                  OverallLikeMe.low)) +
  geom_point(size = 2.5, pch = 21,  color = "black",stroke = 0.7) +
  labs(fill = "Participant Gender") +
  theme(legend.position="none", axis.text.x = element_text(colour = "black", size = 12)) +
  ylab("Percentage Like Me") +
  xlab("") +
  ylim(c(20,80)) +
  geom_hline(yintercept = 50, size =0.5, linetype = 2)+
  theme_cowplot()+
  facet_wrap(~TrialType, labeller = as_labeller(c(GenderTrial='Gender Trials', RaceTrial='Race Trials')))+
  coord_flip()+
  guides(colour="none", fill = "none")+
  # scale_y_continuous(breaks=c(5,25,40,50,60,75,95),
  #                   trans = squish_trans(c(40, 60))) +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )+
  scale_x_discrete(limits=rev)

study4_graph

all_graphs = cowplot::plot_grid(study1_graph,study2_graph,study4_graph, 
                                nrow = 3,ncol=1,align = "v", 
                                labels = c("Expt.1","Expt.2","Expt.3"), 
                                vjust=c(1.7,0.5,0.5),hjust=-0.75,rel_heights = c(1.2,1,1.15))

all_graphs

```

```{r}
#| label: reproduction of original code lines 251-281 to include {here} paths

example_img = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "example_stim.jpeg"))
trial_img = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "Expt1-3_instruct.png"))
trial_img_b = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "Expt1-3_instruct_b.png"))
trial_img_c = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "Expt1-3_Procedure.png"))
portrait_img = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "portrait_matrix_listA.jpg"))
example_img2 = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "example_stimuli.png"))

image_plot = cowplot::plot_grid(ggdraw()+draw_image(example_img),
                                ggdraw()+draw_image(trial_img),ncol = 1,nrow=2,labels =c("A.","B."),rel_heights = c(1,1.8))

image_plot2 = cowplot::plot_grid(ggdraw()+draw_image(portrait_img),
                                 ggdraw()+draw_image(trial_img_b),ncol = 2,nrow=1,labels =c("A.","B."),rel_widths = c(1,1))

image_plot3 = cowplot::plot_grid(ggdraw()+draw_image(portrait_img)+ggplot2::theme(plot.margin = ggplot2::margin(0, 0, 0, 15)),
                                 ggdraw()+draw_image(trial_img_b),ncol = 1,nrow=2,labels =c("A.","B."),rel_heights = c(1,1.8))

image_plot4 = cowplot::plot_grid(ggdraw()+draw_image(example_img2)+ggplot2::theme(plot.margin = ggplot2::margin(0, 0, 0, 15)),
                                 ggdraw()+draw_image(trial_img_c),ncol = 1,nrow=2,labels =c("A.","B."),rel_heights = c(1,1.8))

cowplot::plot_grid(image_plot,
                   all_graphs,ncol = 2,rel_widths = c(1,1.8),labels = c("","C."))


cowplot::plot_grid(image_plot3,
                   all_graphs,ncol = 2,rel_widths = c(1,1.8),labels = c("","C."))

cowplot::plot_grid(image_plot2,
                   all_graphs,ncol = 1,nrow = 2,rel_heights = c(1,1.4),labels = c("","C."))

cowplot::plot_grid(image_plot4,
                   all_graphs,ncol = 2,rel_widths = c(1,1.8),labels = c("","C."))

```

### Code for making the Chinese graph

```{r}
#| label: original code lines 287-345

chinese_data$ConditionLabel = ordered(ifelse(chinese_data$condition == "english","English","Chinese"), levels = c("English","Chinese"))
chinese_data$TrialType = ifelse(chinese_data$picture_condition %in% c("race_male","race_female"),"Race Trials", "Gender Trials")

like_me_averages_subj_study4 <- chinese_data %>%
  dplyr::mutate(OverallLikeMe2 = OverallLikeMe) %>%
  dplyr::group_by(subject,TrialType,ConditionLabel) %>%
  dplyr::summarise(OverallLikeMe.m = 100*mean(OverallLikeMe2))

like_me_averages_summary_study4 <- chinese_data %>%
  dplyr::group_by(subject,TrialType,ConditionLabel) %>%
  dplyr::summarise(OverallLikeMe.m = 100*mean(OverallLikeMe))%>%
  dplyr::group_by(TrialType,ConditionLabel) %>%
  dplyr::summarise(OverallLikeMe.mean = mean(OverallLikeMe.m),
                   OverallLikeMe.sd = sd(OverallLikeMe.m),
                   OverallLikeMe.se = sd(OverallLikeMe.m)/sqrt(length(subject)),
                   OverallLikeMe.high = ci.high(OverallLikeMe.m),
                   OverallLikeMe.low = ci.low(OverallLikeMe.m))

study5_graph <- ggplot(like_me_averages_summary_study4, 
                       aes(x = ConditionLabel,y = OverallLikeMe.mean,fill = ConditionLabel)) +
  #geom_path()+
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_jitter(data = like_me_averages_subj_study4, aes(y = OverallLikeMe.m),alpha = 0.15, size = 1,
              position = position_jitter(width=0.2,height=0)) +
  geom_linerange(color = "black",data = like_me_averages_summary_study4,aes(ymax = OverallLikeMe.high, ymin =
                                                                              OverallLikeMe.low)) +
  geom_point(size = 3, pch = 21,  color = "black",stroke = 0.7) +
  labs(fill = "Participant Gender") +
  theme_cowplot()+
  theme(legend.position="none") +
  ylab("Percentage Like Me") +
  xlab("") +
  ylim(c(20,80))+
  geom_hline(yintercept = 50, size =0.5, linetype = 2)+
  facet_wrap(~TrialType)+
  coord_flip()+
  guides(colour="none")#+
# scale_y_continuous(limits = c(0,100),breaks=c(5,25,40,50,60,75,95),
#                   trans = squish_trans(c(40, 60))) 

study5_graph

trial_img = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "chinese_trial_order.png"))
trial_img2 = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "chinese_trial_order2.png"))
trial_img3 = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "chinese_trial_order3.png"))
trial_img4 = image_read(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "chinese_trial_order4.png"))

cowplot::plot_grid(ggdraw()+draw_image(trial_img),
                   study5_graph,ncol = 2,rel_widths = c(1,1.9),labels = c("A.","B."))

cowplot::plot_grid(ggdraw()+draw_image(trial_img2),
                   study5_graph,ncol = 2,rel_widths = c(1,1.9),labels = c("A.","B."))


cowplot::plot_grid(ggdraw()+draw_image(trial_img4),
                   study5_graph,ncol = 2,rel_widths = c(1,1.9),labels = c("A.","B."))
```

### Code for making the graph combining all the social groups

```{r}
#| label: original code lines 352-427

like_me_groups_subj <- data_for_groups %>%
  dplyr::mutate(OverallLikeMe2 = OverallLikeMe,
                ppt_demog = gsub("_"," ",ppt_demog),
                ppt_demog = ordered(ppt_demog,
                                    levels = c("Asian Man","Asian Woman","White Man","White Woman",
                                               "Black Man","Black Woman"))) %>%
  #filter(TrialType %in% c("RaceTrial","Race Trials")) %>%
  mutate(TrialType = ordered(ifelse(TrialType %in% c("RaceTrial","Race Trials"), "Race Trials","Gender Trials"), levels = c("Race Trials","Gender Trials"))) %>%
  dplyr::group_by(subject,ppt_demog,TrialType) %>%
  dplyr::summarise(OverallLikeMe.m = 100*mean(OverallLikeMe2)) %>%
  mutate(ppt_demog_n = case_when(
    ppt_demog == "Asian Man" ~ "Asian Man\n(n=59)",
    ppt_demog == "Asian Woman" ~ "Asian Woman\n(n=55)",
    ppt_demog == "White Man" ~ "White Man\n(n=145)",
    ppt_demog == "White Woman" ~ "White Woman\n(n=163)",
    ppt_demog == "Black Man" ~ "Black Man\n(n=136)",
    ppt_demog == "Black Woman" ~ "Black Woman\n(n=142)",
    TRUE ~ NA_character_
  ),
  ppt_demog_n = ordered(ppt_demog_n, levels = c("Asian Man\n(n=59)","Asian Woman\n(n=55)","White Man\n(n=145)","White Woman\n(n=163)","Black Man\n(n=136)", "Black Woman\n(n=142)")))

like_me_groups_summary <- data_for_groups %>%
  dplyr::mutate(ppt_demog = gsub("_"," ",ppt_demog),
                ppt_demog = ordered(ppt_demog,
                                    levels = c("Asian Man","Asian Woman","White Man","White Woman",
                                               "Black Man","Black Woman"))) %>%
  #filter(TrialType %in% c("RaceTrial","Race Trials")) %>%
  mutate(TrialType = ordered(ifelse(TrialType %in% c("RaceTrial","Race Trials"), "Race Trials","Gender Trials"), levels = c("Race Trials","Gender Trials"))) %>%
  dplyr::group_by(subject,ppt_demog,TrialType) %>%
  dplyr::summarise(OverallLikeMe.m = 100*mean(OverallLikeMe))%>%
  dplyr::group_by(ppt_demog,TrialType) %>%
  dplyr::summarise(OverallLikeMe.mean = mean(OverallLikeMe.m),
                   OverallLikeMe.sd = sd(OverallLikeMe.m),
                   OverallLikeMe.se = sd(OverallLikeMe.m)/sqrt(length(subject)),
                   OverallLikeMe.high = ci.high(OverallLikeMe.m),
                   OverallLikeMe.low = ci.low(OverallLikeMe.m), 
                   n = n()) %>%
  mutate(ppt_demog_n = case_when(
    ppt_demog == "Asian Man" ~ "Asian Man\n(n=59)",
    ppt_demog == "Asian Woman" ~ "Asian Woman\n(n=55)",
    ppt_demog == "White Man" ~ "White Man\n(n=145)",
    ppt_demog == "White Woman" ~ "White Woman\n(n=163)",
    ppt_demog == "Black Man" ~ "Black Man\n(n=136)",
    ppt_demog == "Black Woman" ~ "Black Woman\n(n=142)",
    TRUE ~ NA_character_
  ),
  ppt_demog_n = ordered(ppt_demog_n, levels = c("Asian Man\n(n=59)","Asian Woman\n(n=55)","White Man\n(n=145)","White Woman\n(n=163)","Black Man\n(n=136)", "Black Woman\n(n=142)")))


groups_graph <- ggplot(like_me_groups_summary, 
                       aes(x = ppt_demog_n,y = OverallLikeMe.mean,fill=ppt_demog_n)) +
  #geom_path()+
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_jitter(data = like_me_groups_subj, aes(y = OverallLikeMe.m),color = "grey",alpha = 0.2, size = 1,
              position = position_jitter(width=0.1,height=0)) +
  geom_linerange(colour = "black",data = like_me_groups_summary,aes(ymax = OverallLikeMe.high, ymin =
                                                                      OverallLikeMe.low)) +
  geom_point(size = 3, pch = 21,  color = "black",stroke = 0.7) +
  theme_cowplot()+
  theme(legend.position="none") +
  ylab("Percentage Like Me") +
  xlab("") +
  ylim(c(20,80)) +
  geom_hline(yintercept = 50, size =0.5, linetype = 2)+
  facet_wrap(~TrialType)+
  coord_flip()+
  guides(colour="none")+
  theme(axis.text = element_text(size = 11),
        axis.title = element_text(size = 12))

#+
#scale_y_continuous(breaks=c(10,25,40,50,60,75,90),
#                   trans = squish_trans(c(35, 65))) 

groups_graph
```

### Code for intuitions graph

```{r}
#| label: original code lines 432-695

# Begin by loading the original set of analyses in file OSF_Analyses

summarised_like_me_data = data_for_groups %>% 
  mutate(syntax_unique = case_when(syntax == "active" ~ "Active\nTransitive",
                                   syntax == "transitive" ~ "Active\nTransitive",
                                   syntax == "conjoined" ~ "Conjoined",
                                   syntax == "passive" ~ "Passive",
                                   syntax == "English Transitive (Chinese speaker)" ~ "English active",
                                   TRUE ~ "Chinese active"),
         subject_unique = paste(study, subject)) %>% 
  group_by(subject_unique,syntax_unique) %>% 
  dplyr::summarise(OverallLikeMe = mean(OverallLikeMe)) %>% 
  group_by(syntax_unique) %>% 
  dplyr::summarise(OverallLikeMe.m = mean(OverallLikeMe), 
                   OverallLikeMe.lo = ci.low(OverallLikeMe),
                   OverallLikeMe.hi = ci.high(OverallLikeMe)) %>%
  mutate(Participant_Background = ifelse(syntax_unique %in% c("Passive","Active\nTransitive","Conjoined"), "English speakers","Chinese speakers"))

summarised_like_me_data_ptpt = data_for_groups %>% 
  mutate(syntax_unique = case_when(syntax == "active" ~ "Active\nTransitive",
                                   syntax == "transitive" ~ "Active\nTransitive",
                                   syntax == "conjoined" ~ "Conjoined",
                                   syntax == "passive" ~ "Passive",
                                   syntax == "English Transitive (Chinese speaker)" ~ "English active",
                                   TRUE ~ "Chinese active"),
         subject_unique = paste(study, subject)) %>% 
  group_by(subject_unique,syntax_unique) %>% 
  dplyr::summarise(OverallLikeMe.m = 100 * mean(OverallLikeMe))  %>%
  mutate(Participant_Background = ifelse(syntax_unique %in% c("Passive","Active\nTransitive","Conjoined"), "English speakers","Chinese speakers"),
         data_type = "Like me effect")


# Intuitions data for participants
intuitions_summary <- intuitions %>%
  dplyr::select(id,subject,list,verb,event,score,condition,test_part) %>%
  dplyr::group_by(subject,verb,condition) %>%
  dplyr::summarise(score = mean(score,na.rm=T)) %>%
  dplyr::group_by(subject,condition) %>%
  dplyr::summarise(score = mean(score,na.rm=T)) %>%
  dplyr::group_by(condition) %>%
  dplyr::summarise(OverallLikeMe.m = mean(score,na.rm=T),
                   OverallLikeMe.lo = ci.low(score),
                   OverallLikeMe.hi = ci.high(score)) %>%
  mutate(Participant_Background = "English speakers", 
         condition = ifelse(condition == "transitive","active",condition),
         data_type = "Communicated Agency",
         predicted_data = "Actual data") %>%
  rename(syntax_unique = condition)  %>% 
  mutate(syntax_unique = case_when(syntax_unique == "active" ~ "Active\nTransitive",
                                   syntax_unique == "transitive" ~ "Active\nTransitive",
                                   syntax_unique == "conjoined" ~ "Conjoined",
                                   syntax_unique == "passive" ~ "Passive"))
intuitions_summary 

intuitions_summary_subj <- intuitions %>%
  dplyr::select(id,subject,list,verb,event,score,condition,test_part) %>%
  dplyr::group_by(subject,verb,condition) %>%
  dplyr::summarise(score = mean(score,na.rm=T)) %>%
  dplyr::group_by(subject,condition) %>%
  dplyr::summarise(OverallLikeMe.m = mean(score,na.rm=T)) %>%
  mutate(Participant_Background = "English speakers", 
         condition = ifelse(condition == "transitive","active",condition),
         data_type = "Communicated Agency",
         predicted_data = "Actual data") %>%
  rename(syntax_unique = condition)%>% 
  mutate(syntax_unique = case_when(syntax_unique == "active" ~ "Active\nTransitive",
                                   syntax_unique == "transitive" ~ "Active\nTransitive",
                                   syntax_unique == "conjoined" ~ "Conjoined",
                                   syntax_unique == "passive" ~ "Passive"))
intuitions_summary_subj 

summary_like_me_and_ratings = summarised_like_me_data %>% 
  mutate(OverallLikeMe.m = OverallLikeMe.m * 100,
         OverallLikeMe.lo = OverallLikeMe.lo * 100,
         OverallLikeMe.hi = OverallLikeMe.hi * 100,
         data_type = "Like me effect",
         predicted_data = "Actual data") %>%
  rbind(intuitions_summary) %>%
  filter(Participant_Background == "English speakers") 

LikeMe_score = ggplot(data = summary_like_me_and_ratings %>% filter(data_type == "Like me effect"),
                      aes(x = syntax_unique, y = OverallLikeMe.m,  group = data_type)) + 
  #geom_hline(yintercept = 0.5,lty =2)+
  geom_line(color = "black")+
  geom_errorbar(color = "black", aes(ymin= OverallLikeMe.lo,ymax = OverallLikeMe.hi), width = 0) +
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_point(aes(fill = syntax_unique),size = 2, pch = 21,  color = "black",stroke = 0.7) +
  #geom_point(size = 2, pch = 21, fill = "grey", color = "black",stroke = 0.7) +
  geom_jitter(data = summarised_like_me_data_ptpt %>% filter(Participant_Background == "English speakers"), size = 1, alpha = 0.03, width = 0.1) +
  facet_grid(Participant_Background ~ data_type, scales = "free")+
  theme_cowplot()+ylim(c(45,60)) + 
  geom_hline(yintercept = 50, lty =2 )+
  xlab("")+ylab("Percentage Like Me\n")+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 12))+
  theme(legend.position="none")+ 
  #      axis.text.x = element_blank(),
  #      axis.ticks.x = element_blank())  +
  theme(
    strip.background.y = element_blank(),
    strip.text.y = element_blank()
  ) + 
  scale_x_discrete(limits=rev) + 
  coord_flip() 


agency_score  = ggplot(data = summary_like_me_and_ratings %>% filter(data_type == "Communicated Agency"),
                       aes(x = syntax_unique, y = OverallLikeMe.m, color = predicted_data,group = data_type)) + 
  #geom_hline(yintercept = 0.5,lty =2)+
  geom_line(color = "black")+
  geom_errorbar(aes(ymin= OverallLikeMe.lo,ymax = OverallLikeMe.hi), width = 0) +
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_point(aes(fill = syntax_unique),size = 2, pch = 21,  color = "black",stroke = 0.7) +  
  geom_jitter(data = intuitions_summary_subj, size = 1, alpha = 0.05, width = 0.1) +
  facet_grid(Participant_Background ~ data_type, scales = "free")+
  theme_cowplot()+ylim(c(-2,1.3)) + geom_hline(yintercept = 0, lty =2 )+
  xlab("")+ylab("Relative agency of\nfirst mentioned") +
  theme(legend.position=c(0.7,0.7), legend.title = element_blank(),
        strip.background.y = element_blank(),
        strip.text.y = element_blank()
  )+scale_color_manual(values = c("black","red"))+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 12))+ 
  theme(legend.position="none", 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())  +
  scale_x_discrete(limits=rev) + 
  coord_flip()
agency_score


empathy_results = empathy_data %>%
  group_by(id, condition) %>%
  dplyr::summarise(empathy_with_first_mentioned = mean(responses)) %>%
  group_by(condition) %>%
  dplyr::summarise(empathy_with_first_mentioned.m = mean(empathy_with_first_mentioned),
                   empathy_with_first_mentioned.sd = sd(empathy_with_first_mentioned),
                   OverallLikeMe.lo = ci.low(empathy_with_first_mentioned),
                   OverallLikeMe.hi = ci.high(empathy_with_first_mentioned)) %>%
  rename(syntax_unique = condition,
         OverallLikeMe.m = empathy_with_first_mentioned.m) %>%
  mutate(data_type = "Speaker Identification",
         Participant_Background = "English speakers")

empathy_results_ptpts = empathy_data %>%
  group_by(id, condition) %>%
  dplyr::summarise(empathy_with_first_mentioned.m = mean(responses)) %>%
  rename(syntax_unique = condition,
         OverallLikeMe.m = empathy_with_first_mentioned.m) %>%
  mutate(data_type = "Speaker Identification",
         Participant_Background = "English speakers")

empathy_score  = ggplot(data = empathy_results,
                        aes(x = syntax_unique, y = OverallLikeMe.m, group = data_type)) + 
  #geom_hline(yintercept = 0.5,lty =2)+
  geom_line(color = "black")+
  geom_errorbar(aes(ymin= OverallLikeMe.lo,ymax = OverallLikeMe.hi), width = 0) +
  scale_color_hue(h = c(270,200))+
  scale_fill_hue(h = c(270,200))+
  geom_point(aes(fill = syntax_unique),size = 2, pch = 21,  color = "black",stroke = 0.7) +  
  geom_jitter(data = empathy_results_ptpts, size = 1, alpha = 0.05, width = 0.1) +
  facet_grid(Participant_Background ~ data_type, scales = "free")+
  theme_cowplot()+ylim(c(-1,2)) + geom_hline(yintercept = 0, lty =2 )+
  xlab("")+ylab("Identification with\nfirst mentioned") +
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 12))+
  theme(strip.background.y = element_blank(),
        strip.text.y = element_blank()
  )+ 
  theme(legend.position="none", 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())  +
  scale_x_discrete(limits=rev) + 
  coord_flip()


intuitions_graph = cowplot::plot_grid(LikeMe_score,agency_score, empathy_score,
                   nrow = 1,ncol = 3, rel_widths = c(0.4,0.3,0.3))


cowplot::plot_grid(intuitions_graph,groups_graph, nrow = 2, 
                   rel_heights = c(0.35,0.65), labels = "AUTO")


```

## Code for statistical analyses

"Note that Study 3 in the paper is referred to as Study 4 in this dataset - a legacy of when the data was collected for Brough's thesis." (comment from original script).

It would be interesting to know why the original Study 3 is not reported in the paper.

```{r}
#| label: original code lines 625-627

data1 = subset(data, study == "study1")
data2 = subset(data, study == "study2")
data4 = subset(data, study == "study4")
```

### Study 1

```{r}
#| label: original code lines 634-688

data1_overallMeans = data1 %>% 
  dplyr::group_by(subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by() %>% 
  dplyr::summarise(OverallLikeMe.m = mean(OverallLikeMe), OverallLikeMe.low = ci.low(OverallLikeMe),OverallLikeMe.high = ci.high(OverallLikeMe))

data1_overallMeans

data1_demog_overallMeans = data1 %>% 
  dplyr::group_by(ppt_demog,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_demog) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data1_demog_overallMeans

data1$syntax = as.factor(as.character(data1$syntax))
contrasts(data1$syntax)[1] = -1
data1_overallAnalysis = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                      data = data1, family = "binomial"))

# Replication team: This model returns singular fit warning:
data1_overallAnalysis_wm = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data1, ppt_demog == "White_Man"), family = "binomial"))
data1_overallAnalysis_wm

# Replication team: This model also returns singular fit warning:
data1_overallAnalysis_ww = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data1, ppt_demog == "White_Woman"), family = "binomial"))
data1_overallAnalysis_ww

# Replication team: This model also returns singular fit warning:
data1_overallAnalysis_bm = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data1, ppt_demog == "Black_Man"), family = "binomial"))
data1_overallAnalysis_bm

# Replication team: This model returns singular fit warning:
data1_overallAnalysis_bw = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data1, ppt_demog == "Black_Woman"), family = "binomial"))
data1_overallAnalysis_bw

data1_gender_race = data1 %>% 
  dplyr::group_by(TrialType,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(TrialType) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data1_gender_race

# Replication team: This model also returns singular fit warning:
data1_overallAnalysis_gender = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                             data = subset(data1, TrialType != "RaceTrial"), family = "binomial"))
data1_overallAnalysis_gender

# Replication team: This model also returns singular fit warning:
data1_overallAnalysis_race = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                           data = subset(data1, TrialType == "RaceTrial"), family = "binomial"))
data1_overallAnalysis_race

data1_syntax = data1 %>% 
  dplyr::group_by(syntax,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(syntax) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))
data1_syntax
```

### Study 2

```{r}
#| label: original code lines 693-747

data2_overallMeans = data2 %>% 
  dplyr::group_by(subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by() %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data2_overallMeans

data2_demog_overallMeans = data2 %>% 
  dplyr::group_by(ppt_demog,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_demog) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data2_demog_overallMeans

data2$syntax = as.factor(as.character(data2$syntax))
contrasts(data2$syntax)[1] = -1

data2_overallAnalysis = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                      data = data2, family = "binomial"))
data2_overallAnalysis

data2_overallAnalysis_wm = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data2, ppt_demog == "White_Man"), family = "binomial"))
data2_overallAnalysis_wm

# Replication team: This model returns a singularity warning:
data2_overallAnalysis_ww = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data2, ppt_demog == "White_Woman"), family = "binomial"))
data2_overallAnalysis_ww

# Replication team: This model also returns a singularity warning:
data2_overallAnalysis_bm = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data2, ppt_demog == "Black_Man"), family = "binomial"))
data2_overallAnalysis_bm

# Replication team: This model returns a singularity warning:
data2_overallAnalysis_bw = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data2, ppt_demog == "Black_Woman"), family = "binomial"))
data2_overallAnalysis_bw

data2_gender_race = data2 %>% 
  dplyr::group_by(TrialType,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(TrialType) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data2_gender_race

# Replication team: This model also returns a singularity warning:
data2_overallAnalysis_gender = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                             data = subset(data2, TrialType != "RaceTrial"), family = "binomial"))
data2_overallAnalysis_gender

# Replication team: This model also returns a singularity warning:
data2_overallAnalysis_race = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                           data = subset(data2, TrialType == "RaceTrial"), family = "binomial"))
data2_overallAnalysis_race

data2_syntax = data2 %>% 
  dplyr::group_by(syntax,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(syntax) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))
data2_syntax
```
Replication team: As a robustness check, we computed the preregistered models which were not included in the analysis code, each for gender and race

```{r}
#| label: robustness check Study 2: Participant Gender and Race as fixed effects on gender trials

prereg_mod1_gender <- glmer(OverallLikeMe ~ ppt_gender * ppt_race
  + (1 | subject)
  + (1 + ppt_gender + ppt_race | event),
  data = subset(data2, TrialType == "GenderTrial"),
  family = "binomial")

summary(prereg_mod1_gender)

# Removing random slope at event level
prereg_mod1_gender <- glmer(OverallLikeMe ~ ppt_gender * ppt_race
  + (1 | subject)
  + (1 | event),
  data = subset(data2, TrialType == "GenderTrial"),
  family = "binomial")

# Removing all random effects for convergance
prereg_mod1_gender_converge <- glm(OverallLikeMe ~ ppt_gender * ppt_race,
                            data = subset(data2, TrialType == "GenderTrial"),
                            family = "binomial")

summary(prereg_mod1_gender_converge)
tab_model(prereg_mod1_gender_converge)

emmeans(prereg_mod1_gender_converge, ~ ppt_gender + ppt_race, type = "response")
pairs(emmeans(prereg_mod1_gender_converge, ~ ppt_gender + ppt_race, type = "response"))

```

```{r}
#| label: robustness check Study 2: Participant Gender and Race as fixed effects on race trials

prereg_mod1_race <- glmer(OverallLikeMe ~ ppt_gender * ppt_race
                     + (1 | subject)
                     + (1 + ppt_gender + ppt_race | event),
                     data = subset(data2, TrialType == "RaceTrial"),
                     family = "binomial")

summary(prereg_mod1_race)

# Removing random effects for convergance
prereg_mod1_race_converge <- glm(OverallLikeMe ~ ppt_gender * ppt_race,
                                   data = subset(data2, TrialType == "RaceTrial"),
                                   family = "binomial")

summary(prereg_mod1_race_converge)
tab_model(prereg_mod1_race_converge)

```

### Study 3

```{r}
#| label: original code lines 751-805

data4_overallMeans = data4 %>% 
  dplyr::group_by(subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by() %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data4_overallMeans

data4_demog_overallMeans = data4 %>% 
  dplyr::group_by(ppt_demog,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_demog) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data4_demog_overallMeans

data4$syntax = as.factor(as.character(data4$syntax))
contrasts(data4$syntax)[1] = -1
data4_overallAnalysis = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                      data = data4, family = "binomial"))
data4_overallAnalysis
data4_overallAnalysis_wm = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data4, ppt_demog == "White_Man"), family = "binomial"))
data4_overallAnalysis_wm
data4_overallAnalysis_ww = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data4, ppt_demog == "White_Woman"), family = "binomial"))
data4_overallAnalysis_ww
data4_overallAnalysis_bm = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data4, ppt_demog == "Black_Man"), family = "binomial"))
data4_overallAnalysis_bm
data4_overallAnalysis_bw = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                         data = subset(data4, ppt_demog == "Black_Woman"), family = "binomial"))
data4_overallAnalysis_bw

data4_gender_race = data4 %>% 
  dplyr::group_by(TrialType,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(TrialType) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data4_gender_race
data4_overallAnalysis_gender = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                             data = subset(data4, TrialType != "RaceTrial"), family = "binomial"))
data4_overallAnalysis_gender

data4_overallAnalysis_race = summary(glmer(OverallLikeMe ~ 1 + syntax + (1+syntax|subject) + (1+syntax|event), 
                                           data = subset(data4, TrialType == "RaceTrial"), family = "binomial"))
data4_overallAnalysis_race

data4_syntax = data4 %>% 
  dplyr::group_by(syntax,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(syntax) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))
data4_syntax
```

Replication team: As a robustness check, we computed the preregistered models which were not included in the analysis code for both gender and race:

```{r}
#| label: robustness check Study 3 gender

model_gender_prereg <- glmer(OverallLikeMe ~  ppt_gender * syntax + (1 + syntax | subject) + (1 + ppt_gender | event),
                             data = subset(data4, TrialType == "GenderTrial"),
                             family = binomial(link = "logit"),
                             control = glmerControl(optimizer = "bobyqa")
)
summary(model_gender_prereg)

tab_model(model_gender_prereg)

```

```{r}
#| label: robustness check Study 3 race

model_race_prereg <- glmer(OverallLikeMe ~  ppt_race * syntax + (1 + syntax | subject) + (1 + ppt_race | event),
                             data = subset(data4, TrialType == "RaceTrial"),
                             family = binomial(link = "logit"),
                             control = glmerControl(optimizer = "bobyqa")
)
summary(model_race_prereg)

tab_model(model_race_prereg)
```

```{r}
#| label: compute M following original code lines 785-791

data4_gender_race_prereg = data4 %>% 
  dplyr::group_by(TrialType,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(TrialType) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data4_gender_race_prereg
```

When removing the random effect of event, the model computes without the optimizer.

```{r}
#| label: robustness check Study 3 gender without optimizer
 
model_gender_prereg2 <- glmer(OverallLikeMe ~  ppt_gender * syntax + (1 + syntax | subject),
                              data = subset(data4, TrialType == "GenderTrial"),
                              family = binomial(link = "logit")
)
summary(model_gender_prereg2)

tab_model(model_gender_prereg2)

```

```{r}
#| label: robustness check Study 3 race without optimizer

model_race_prereg2 <- glmer(OverallLikeMe ~  ppt_race * syntax + (1 + syntax | subject),
                             data = subset(data4, TrialType == "RaceTrial"),
                             family = binomial(link = "logit"),
)

summary(model_race_prereg2)

tab_model(model_race_prereg2)
```

### Chinese study

```{r}
#| label: original code lines 810-833

data5_overallMeans = chinese_data %>% 
  dplyr::group_by(subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by() %>% 
  dplyr::summarise(OverallLikeMe.m = mean(OverallLikeMe), OverallLikeMe.low = ci.low(OverallLikeMe),OverallLikeMe.high = ci.high(OverallLikeMe))

data5_overallMeans

data5_demog_overallMeans = chinese_data %>% 
  dplyr::group_by(ppt_gender,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_gender) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data5_demog_overallMeans


data5_condition_overallMeans = chinese_data %>% 
  dplyr::group_by(condition,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(condition) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data5_condition_overallMeans
```

Reproduction team: original code lines 810-833: minor differences becaus of the bootstrap "data5_overallMeans" refers to the overall effect "data5_demog_overallMeans" outputs the numbers for the man and women overall "data5_condition_overallMeans" differentiates between the chinese overall and the english overall

```{r}
#| label: reproduction code lines 834-848

# Reproduction team: code to reproduce the results of the paper

overall_like_me <- glmer(OverallLikeMe ~ 1+condition+ (1|subject) + (1|verb), 
                         data = subset(chinese_data), 
                         family = "binomial")

summary(overall_like_me)
```

It was necessary to write reproduction code lines 834-848 to reproduce the numbers mentioned in the paper (size effect of the overall like-me effect).

```{r}
#| label: original code lines 834-848

overall_like_me_English <- glmer(OverallLikeMe ~ 1+ (1|subject) + (1|verb), 
                                 data = subset(chinese_data, condition == "english"), 
                                 family = "binomial")

summary(overall_like_me_English)


overall_like_me_Chinese <- glmer(OverallLikeMe ~ 1+ (1|subject) + (1|verb), 
                                 data = subset(chinese_data, condition == "chinese"), 
                                 family = "binomial")

summary(overall_like_me_Chinese)
```

Reproduction team: original code lines 834-848: size effect for English as an additional language and natively producing Chinese

```{r}
#| label: original code lines 849-865

overall_like_me_male <- glmer(OverallLikeMe ~ 1+condition+ (1|subject) + (1+condition|verb), 
                              data = subset(chinese_data, ppt_gender == "man"), 
                              family = "binomial")

summary(overall_like_me_male)


overall_like_me_female <- glmer(OverallLikeMe ~ 1+condition+ (1|subject) + (1+condition|verb), 
                                data = subset(chinese_data, ppt_gender == "woman"), 
                                family = "binomial")

summary(overall_like_me_female)
```

Reproduction team: original code lines 849-865: those numbers are not reported in the paper for experiment 4

```{r}
#| label: additional code neutral names


names_neutral <- chinese_data |> 
    filter(!left_name %in% c("霍普", "贝斯")) |> 
  filter(!right_name %in% c("霍普", "贝斯")) 

left_name_not_neutral <- chinese_data |> 
  filter(left_name %in% c("霍普", "贝斯")) #673

right_name_not_neutral <- chinese_data |> 
  filter(right_name %in% c("霍普", "贝斯"))  #674


names_neutral |> 
  filter(right_name == "贝斯") |> 
  nrow()

names_neutral |> 
  filter(left_name == "贝斯") |> 
  nrow()

names_neutral |> 
  filter(right_name == "霍普") |> 
  nrow()

names_neutral |> 
  filter(left_name == "霍普") |> 
  nrow()

```

Reproduction team: additional code neutral names First, we excluded the neutral names "霍普", "贝斯" from the data and saved it as "names_neutral". Then we double checked, to be sure that the neutral names "霍普", "贝斯" aren't in our new dataset "names_neutral".

```{r}
#| label: additional code neutral names robustness


data5_condition_overallMeans_neutral = names_neutral %>% 
  dplyr::group_by(condition,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(condition) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data5_condition_overallMeans_neutral

overall_like_me_Chinese_neutral <- glmer(OverallLikeMe ~ 1+ (1|subject) + (1|verb), 
                                 data = subset(names_neutral, condition == "chinese"), 
                                 family = "binomial")

summary(overall_like_me_Chinese_neutral)


# overall like me for the condition "chinese" + size effect

###
data5_overallMeans_neutral = names_neutral %>% 
  dplyr::group_by(subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by() %>% 
  dplyr::summarise(OverallLikeMe.m = mean(OverallLikeMe), OverallLikeMe.low = ci.low(OverallLikeMe),OverallLikeMe.high = ci.high(OverallLikeMe))

data5_overallMeans_neutral

overall_like_me_neutral <- glmer(OverallLikeMe ~ 1+condition+ (1|subject) + (1|verb), 
                         data = subset(names_neutral), 
                         family = "binomial")

summary(overall_like_me_neutral)

# overall like me effect without neutral names

###

data5_condition_LikeMeGender_neutral_means = names_neutral |> 
  dplyr::group_by(condition,subject) |> 
  dplyr::summarise(LikeMeGender = 100 *  mean(LikeMeGender)) |> 
  dplyr::group_by(condition) |> 
  dplyr::summarise(LikeMeGender.m = round(mean(LikeMeGender),1), LikeMeGender.low = round(ci.low(LikeMeGender),1),LikeMeGender.high = round(ci.high(LikeMeGender),1))

data5_condition_LikeMeGender_neutral_means


### Like me gender effect for chinese and english condition without neutral names

data5_condition_LikeMeGender_means = chinese_data |> 
  dplyr::group_by(condition,subject) |> 
  dplyr::summarise(LikeMeGender = 100 *  mean(LikeMeGender)) |> 
  dplyr::group_by(condition) |> 
  dplyr::summarise(LikeMeGender.m = round(mean(LikeMeGender),1), LikeMeGender.low = round(ci.low(LikeMeGender),1),LikeMeGender.high = round(ci.high(LikeMeGender),1))

data5_condition_LikeMeGender_means

### Like me gender effect for chinese and english condition with neutral names


data5_demog_overallMeans_neutral = names_neutral %>% 
  dplyr::group_by(ppt_gender,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_gender) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

data5_demog_overallMeans_neutral

### overall like me for men and women
```

Reproduction team: additional code neutral names robustness: code to check, whether the like-me effect increases when neutral names are excluded.

### Analysis of Intuitions/Rating study

```{r}
#| label: original code lines 868-930
# datafile was read in earlier

data_summary_participant <- intuitions %>%
  dplyr::select(id,subject,list,verb,event,score,condition,test_part) %>%
  dplyr::group_by(subject,verb,condition) %>%
  dplyr::summarise(score = mean(score,na.rm=T)) %>%
  dplyr::group_by(subject,condition) %>%
  dplyr::summarise(score = mean(score,na.rm=T)) %>%
  dplyr::group_by(condition) %>%
  dplyr::summarise(score.m = mean(score,na.rm=T),
                   score.sd = sd(score,na.rm=T),
                   score.low = ci.low(score),
                   score.high = ci.high(score)) 
data_summary_participant


data_avgd_trial <- intuitions %>%
  dplyr::select(id,subject,list,verb,event,score,condition,test_part) %>%
  dplyr::group_by(subject,verb,event,condition) %>%
  dplyr::summarise(score = mean(score,na.rm=T))


avgd_ratings_conj = lmer(score ~ 1 + (1|subject) + (1|event), 
                         data = subset(data_avgd_trial, condition == "conjoined"))

avgd_ratings_conj.0 = lmer(score ~ 0 + (1|subject) + (1|event), 
                           data = subset(data_avgd_trial, condition == "conjoined"))

summary(avgd_ratings_conj)
anova(avgd_ratings_conj,avgd_ratings_conj.0)


avgd_ratings_tran = lmer(score ~ 1 + (1|subject) + (1|event), 
                         data = subset(data_avgd_trial, condition == "transitive"))

avgd_ratings_tran.0 = lmer(score ~ 0 + (1|subject) + (1|event), 
                           data = subset(data_avgd_trial, condition == "transitive"))

summary(avgd_ratings_tran)
anova(avgd_ratings_tran,avgd_ratings_tran.0)

avgd_ratings_passive = lmer(score ~ 1 + (1|subject) + (1|event), 
                         data = subset(data_avgd_trial, condition == "passive"))
avgd_ratings_passive.0 = lmer(score ~ 0 + (1|subject) + (1|event), 
                           data = subset(data_avgd_trial, condition == "passive"))

summary(avgd_ratings_passive)
anova(avgd_ratings_passive,avgd_ratings_passive.0)

# Preregistration here https://aspredicted.org/7698v.pdf
intuitions$test_part = as.factor(intuitions$test_part)
contrasts(intuitions$test_part)[1] = -1
avgd_ratings = lmer(score ~ 1 +  condition*test_part + (1+test_part|subject) + (1|event), 
                            data = intuitions)

summary(avgd_ratings)

avgd_ratings.1 = lmer(score ~ 1 +  condition+test_part + (1+test_part|subject) + (1|event), 
                    data = intuitions)
avgd_ratings.0 = lmer(score ~ 1  + test_part +(1+test_part|subject) + (1|event), 
                      data = intuitions)

anova(avgd_ratings.1,avgd_ratings.0)

# See analysis of omnibus data for the comparison of like me over constructions
```

### Analysis of empathy data

```{r}
# https://aspredicted.org/7698v.pdf

empathy_grammar = lmer(responses ~ 1 +  condition + (1+condition|subject) + (1|verb), 
     data = empathy_data)
summary(empathy_grammar)
empathy_grammar.0 = lmer(responses ~ 1 + (1|subject) + (1|verb), 
                       data = empathy_data)
anova(empathy_grammar,empathy_grammar.0)
```

### Analysis of omnibus data

```{r}
#| label: original code lines 948-1031

data_for_groups = data_for_groups %>% 
  mutate(TrialType = ordered(ifelse(TrialType %in% c("RaceTrial","Race Trials"), "Race Trials","Gender Trials"), levels = c("Race Trials","Gender Trials")))
data_for_groups$ppt_gender = as.character(data_for_groups$ppt_gender)
data_for_groups[data_for_groups$ppt_demog == "Asian Man",]$ppt_gender = "man"
data_for_groups[data_for_groups$ppt_demog == "Asian Woman",]$ppt_gender = "woman"

data_for_groups$ppt_race = as.character(data_for_groups$ppt_race)
data_for_groups[data_for_groups$ppt_demog == "Asian Man",]$ppt_race = "asian"
data_for_groups[data_for_groups$ppt_demog == "Asian Woman",]$ppt_race = "asian"

data_for_groups$ppt_race = factor(data_for_groups$ppt_race, levels = c("white","black","asian"))
data_for_groups$ppt_gender = factor(data_for_groups$ppt_gender, levels = c("man","woman"))

data_for_groups %>% 
  dplyr::group_by(ppt_demog,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_demog) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

print("for gender alone")
data_for_groups %>% filter(TrialType == "Gender Trials") %>%
  dplyr::group_by(ppt_gender,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_gender) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

print("for gender alone")
data_for_groups %>% filter(TrialType == "Gender Trials") %>%
  dplyr::group_by(ppt_race, ppt_gender,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(ppt_race, ppt_gender) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))


# Set contrasts
# Race
c_race<-contr.treatment(3)
race_codes<-matrix(rep(1/3, 6), ncol=2)
race_contrasts = c_race - race_codes
contrasts(data_for_groups$ppt_race) <- race_contrasts

# Gender

c_gender<-contr.treatment(2)
gender_codes<-matrix(rep(1/2, 2), ncol=1)
gender_contrasts = c_gender - gender_codes
contrasts(data_for_groups$ppt_gender) <- gender_contrasts

demographic_comparison_gender = summary(glmer(OverallLikeMe ~ 1 + ppt_gender*ppt_race + (1|subject) ,  # Have to get rid of random slopes for events by race because some events were only in the Asian study. And end up removing by event random effects altogether for convergence
                                              data = subset(data_for_groups, TrialType == "Gender Trials"), family = "binomial"))
demographic_comparison_gender


demographic_comparison_race = summary(glmer(OverallLikeMe ~ 1 + ppt_gender*ppt_race + (1|subject) ,   # Have to get rid of random slopes for events by race because some events were only in the Asian study. And end up removing by event random effects altogether for convergence
                                            data = subset(data_for_groups, TrialType == "Race Trials"), family = "binomial"))
demographic_comparison_race



black_women_gender = summary(glmer(OverallLikeMe ~ 1  + (1|subject) ,  # Have to get rid of random slopes for events by race because some events were only in the Asian study. And end up removing by event random effects altogether for convergence
                                   data = subset(data_for_groups, TrialType == "Gender Trials" & ppt_gender == "woman" & ppt_race == "black"), family = "binomial"))
black_women_gender


data_for_groups %>% 
  dplyr::group_by(TrialType,subject) %>% 
  dplyr::summarise(OverallLikeMe = 100 *  mean(OverallLikeMe)) %>% 
  dplyr::group_by(TrialType) %>% 
  dplyr::summarise(OverallLikeMe.m = round(mean(OverallLikeMe),1), OverallLikeMe.low = round(ci.low(OverallLikeMe),1),OverallLikeMe.high = round(ci.high(OverallLikeMe),1))

trial_type_comparison  = summary(glmer(OverallLikeMe ~ 1 + TrialType + (1+TrialType|subject) + (1+TrialType|event), 
                                       data = data_for_groups, family = "binomial"))
trial_type_comparison 

# Test of grammar
likeme_grammar = lmer(OverallLikeMe ~ 1 +  syntax + (1|subject) + (1|verb), 
                       data = data_for_groups %>% filter(ppt_race != "asian") %>% mutate(syntax = ifelse(syntax == "active","transitive",syntax)))
summary(likeme_grammar)

likeme_grammar.0 = lmer(OverallLikeMe ~ 1  + (1|subject) + (1|verb), 
                      data = data_for_groups %>% filter(ppt_race != "asian") %>% mutate(syntax = ifelse(syntax == "active","transitive",syntax)))
summary(likeme_grammar.0)

anova(likeme_grammar,likeme_grammar.0)

```
