---
title: "Reproduction of the overall memory data analysis"
date: last-modified
freeze: true
cache: true
format:
  html:
    embed-resources: true
    number-sections: true
    toc: true
---

# Code for pre-registered analysis of memory game response times in experiments 1 thru 3

```{r}
# Analysis of loaded full_memory data
library(tidyverse)
library(cowplot)
library(lme4)

# From Mike Frank
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)} #  mean(x,na.rm=na.rm) -
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) } #-

```

```{r}
memory = read_csv(here("R_scripts", "scripts_reproduction" ,"Data_Preprocessing_reproduction", "reproduced_data", "studies1_2_3_memory.csv"))

```

```{r}
memory$figure_gender = ifelse(grepl("W[1-2].jpg",memory$stimulus), "woman","man")

memory$figure_race = ifelse(grepl("W[MW][1-2].jpg",memory$stimulus), "white","black")

memory = memory %>%
  dplyr::mutate(first_guess_num = ifelse(first_guess == "TRUE",1,0),
                correct_response = ifelse(button_pressed == correct,1,0),
                rt = as.numeric(rt))

memory %>%
  filter(first_guess == "TRUE" & correct_response == 1) %>%
  dplyr::group_by(ppt_gender,figure_gender,figure_race) %>%
  dplyr::mutate(first_guess_num = ifelse(first_guess == "TRUE",1,0),
                rt = as.numeric(rt)) %>%
  dplyr::summarise(mean(first_guess_num),
                   mean((rt)))

memory$like_me_gender = ifelse(memory$ppt_gender == memory$figure_gender,1,0)

memory$like_me_race = ifelse(memory$ppt_race == memory$figure_race,1,0)

memory$OverallLikeMe = ifelse(memory$ppt_race == memory$figure_race & memory$ppt_gender == memory$figure_gender, 1, 0)

memory$LikeMeFeature = ifelse(memory$ppt_race == memory$figure_race & memory$ppt_gender == memory$figure_gender, "Gender Match\nRace Match", 
                              ifelse(memory$ppt_race != memory$figure_race & memory$ppt_gender == memory$figure_gender, "Gender Match\nRace No-Match",
                                     ifelse(memory$ppt_race == memory$figure_race & memory$ppt_gender != memory$figure_gender, "Gender No-Match\nRace Match","Gender No-Match\nRace No-Match")))

#Replication team: We believe that the code below means that -1 corresponds to the highest me-likeness, whereas 1 corresponds to lowest me-likeness

memory$LikeMeFeatureNumeric = ifelse(memory$ppt_race == memory$figure_race & memory$ppt_gender == memory$figure_gender, -1, 
                              ifelse(memory$ppt_race != memory$figure_race & memory$ppt_gender == memory$figure_gender, 0,
                                     ifelse(memory$ppt_race == memory$figure_race & memory$ppt_gender != memory$figure_gender, 0,1)))

```

Replication team: The following code chunk means that the authors' models are computed with like_me_race as a numeric variable. But as they are binary, that's probably okay?

```{r}
summary(lmer(log(rt) ~ like_me_race + (1+like_me_race|id), data = memory %>% 
               filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1)))

summary(lmer(log(rt) ~ like_me_gender + (1+like_me_gender|id), 
             data = memory %>% filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1)))

summary(lmer(log(rt) ~ OverallLikeMe + (1+OverallLikeMe|id), 
             data = memory %>% filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1)))

summary(lmer(log(rt) ~ LikeMeFeatureNumeric + (1+LikeMeFeatureNumeric|id), 
             data = memory %>% filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1)))

numeric = lmer(log(rt) ~ LikeMeFeatureNumeric + (1+LikeMeFeatureNumeric|id), 
     data = memory %>% filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1))

summary(numeric)

# Replication team: The summary function of the lmer() function does not report p-values by default so we used the following package and function to get the coefficient p-values:
library(sjPlot)
tab_model(numeric)

library(emmeans)
emmeans(object = numeric, 
        specs = "LikeMeFeatureNumeric",
        infer = TRUE)

numeric_base = lmer(log(rt) ~ 1 + (1|id), 
               data = memory %>% filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1))

anova(numeric,numeric_base)

```

```{r}
memory_means = memory %>%
  filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1) %>%
  dplyr::group_by(id, LikeMeFeature) %>%
  dplyr::summarise(rt = median(rt,na.rm = T)) %>%
  dplyr::mutate(rt_norm = rt - mean(rt)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(LikeMeFeature) %>%
  dplyr::mutate(rt_norm = rt_norm + mean(rt)) %>%
  dplyr::summarise(rt.m = mean(rt),
                   se = sd(rt)/sqrt(n()),
                   se.norm = sd(rt_norm)/sqrt(n()), # within subject SE
                   ci.norm = 1.96 * se.norm,# within subject CI
                   rt.low = ci.low(rt),# Remember that the bootstrapped CIs do not account for within subjects design
                   rt.high = ci.high(rt)) # Remember that the bootstrapped CIs do not account for within subjects design
memory_means

memory_subj = memory %>%
  filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1) %>%
  dplyr::group_by(id, LikeMeFeature) %>%
  dplyr::summarise(rt.m = mean(rt,na.rm = T))

ggplot(memory_subj,
       aes(x = LikeMeFeature,
           y = rt.m,
           color = LikeMeFeature))+
  geom_jitter(alpha = 0.05)+
  #scale_y_continuous(trans='log2')+
  coord_flip()+
  theme_cowplot()+ 
  theme(legend.position = "none")+
  #geom_point(data = memory_means, size = 3)+
  ylim(c(1800,4500))+
  scale_x_discrete(limits=rev)+
  geom_crossbar(data = memory_means,aes(ymin = rt.m, ymax = rt.m), 
                width = 0.7)+
  geom_linerange(data = memory_means,aes(ymin = rt.m - ci.norm, 
                                         ymax = rt.m + ci.norm),
                 lwd = 1)+
  ylab("Time to choose name (ms)")+xlab("")

#ggsave(file = here("R_scripts", "scripts_reproduction", "Data_Analysis_reproduction", "Plots","memory_subj_original.svg"))
```

## Reproduction team: Robustness tests

We begin by illustrating all the data points entered in the model above with an adjusted version of the plot above:

```{r}
ggplot(memory_subj,
       aes(x = LikeMeFeature,
           y = rt.m,
           color = LikeMeFeature))+
  geom_boxplot(outliers = FALSE)+  
  geom_jitter(alpha = 0.1, width = 0.2)+
  #scale_y_continuous(trans='log2')+
  coord_flip()+
  theme_cowplot()+ 
  theme(legend.position = "none")+
  scale_x_discrete(limits=rev)+
  ylab("Time to choose name (ms)")+xlab("")

#ggsave(file = here("R_scripts", "scripts_reproduction", "Data_Analysis_reproduction", "Plots","memory_subj_boxplots.svg"))
```

We decided to model the LikeMeFeature as an ordinal categorical variable rather than as a numeric variable. The model does not converge unless we use an optimizer. As above, we also added a comparison of the predicted means using the {emmeans} package. The results match closely those of the original analysis.

```{r}
#| label: Robustness test by replication team

numeric.ordinal = lmer(log(rt) ~ ordered(LikeMeFeatureNumeric) + (1+LikeMeFeatureNumeric|id), 
                       control = lmerControl(optimizer = "bobyqa"),
               data = memory %>% filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1))

summary(numeric.ordinal)

emmeans(object = numeric.ordinal, 
        specs = "LikeMeFeatureNumeric",
        infer = TRUE)
```

In the original analysis, the authors removed trials for which participants needed longer than 10 s to name the images (as preregistered). Below are the descriptive statistics of the response time variable for the trials that are included in this analysis (first guesses only and correct responses only). It turns out that 10,000 is much longer than most people needed:

```{r}
memory |> 
  filter(first_guess == "TRUE" & correct_response == 1) |> 
  pull(rt) |> 
  summary()
```

In our robustness test, we exclude trials for which the response time was longer than 5,000 ms, which corresponds to a bit more than what is displayed on the descriptive plot included in this script (see above).

```{r}
memory.robustness <- memory |> 
  filter(first_guess == "TRUE" & rt < 6000 & correct_response == 1)

memory.analysis <- memory |> 
  filter(first_guess == "TRUE" & rt < 10000 & correct_response == 1)

# This means that we are retaining 91% of the data used in the original analysis
nrow(memory.robustness)/nrow(memory.analysis)*100
```


```{r}
memory.robustness_means = memory.robustness %>%
  dplyr::group_by(id, LikeMeFeature) %>%
  dplyr::summarise(rt = median(rt,na.rm = T)) %>%
  dplyr::mutate(rt_norm = rt - mean(rt)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(LikeMeFeature) %>%
  dplyr::mutate(rt_norm = rt_norm + mean(rt)) %>%
  dplyr::summarise(rt.m = mean(rt),
                   se = sd(rt)/sqrt(n()),
                   se.norm = sd(rt_norm)/sqrt(n()), # within subject SE
                   ci.norm = 1.96 * se.norm,# within subject CI
                   rt.low = ci.low(rt),# Remember that the bootstrapped CIs do not account for within subjects design
                   rt.high = ci.high(rt)) # Remember that the bootstrapped CIs do not account for within subjects design

memory.robustness_means # The results are consistent with the reported findings.

memory_subj.robustness = memory.robustness |> 
  dplyr::group_by(id, LikeMeFeature) |> 
  dplyr::summarise(rt.m = mean(rt,na.rm = T))

ggplot(memory_subj.robustness,
       aes(x = LikeMeFeature,
           y = rt.m,
           color = LikeMeFeature))+
  geom_boxplot(outliers = FALSE)+  
  geom_jitter(alpha = 0.1, width = 0.2)+
  #scale_y_continuous(trans='log2')+
  coord_flip()+
  theme_cowplot()+ 
  theme(legend.position = "none")+
  scale_x_discrete(limits=rev)+
  ylab("Time to choose name (ms)")+xlab("")

```

```{r}
numeric.robustness = lmer(log(rt) ~ LikeMeFeatureNumeric + (1+LikeMeFeatureNumeric|id), 
     data = memory.robustness)

summary(numeric.robustness)

base.robustness = lmer(log(rt) ~ 1 + (1|id), 
               data = memory.robustness)

anova(numeric.robustness, base.robustness)


ordered.robustness = lmer(log(rt) ~ ordered(LikeMeFeatureNumeric) + (1+LikeMeFeatureNumeric|id), 
     data = memory.robustness)

summary(ordered.robustness)

emmeans(object = ordered.robustness, 
        specs = "LikeMeFeatureNumeric",
        infer = TRUE)


```

