---
title: "Processing of data collected as part of the rating studies"
format: html
editor: visual
---

Original file path: osfstorage-archive/Data Preprocessing/EmpathyStudy/process_data.R

```{r}
#| label: original code lines 1-6
 
# From Mike Frank
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)} #  mean(x,na.rm=na.rm) -
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) } #-

```

```{r, message=FALSE}
#| label: original code line 8

library(dplyr)

```

We added code for imports of the libraries needed to run the original script:

```{r, message=FALSE}

library(lme4)
library(readr)
library(ggplot2)
library(cowplot)
library(here)

```

We adjusted the original code to use the {here} library for importing the data to ensure that our R project has robust relative file paths:

```{r}
#| label: reproduction of code lines 10-12 to include {here} path

files <- list.files(path = here("R_scripts/scripts_and_data_original/Data_Preprocessing_original/EmpathyStudy/full_empathy_data"), pattern = "\\.csv$", full.names = TRUE)
raw_data <- sapply(files, read_csv, simplify=FALSE) %>% 
  bind_rows(.id = "id")

```

The raw data that the authors provided are already processed/anonymised:

```{r}
#| label: original code lines 13-29

test = raw_data %>% # Read in data
  dplyr::filter(trial_type == "survey-likert-extra-labels" )%>%
  mutate(responses = gsub('{\"Q0\":','',
                          x=responses
                          ,fixed=T),
         responses = gsub('}','',
                          x=responses
                          ,fixed=T),
         responses = as.numeric(responses)-3,
         responses = ifelse(is.na(name_order), responses, ifelse(name_order == "right_to_left", responses,-1 *responses))
                            ) %>%
  mutate(condition = case_when(
    grepl("_active",verb, fixed = TRUE) ~ "active",
    grepl("_passive",verb, fixed = TRUE) ~ "passive",
    grepl("_conjoined",verb, fixed = TRUE) ~ "conjoined",
    TRUE ~ "catch"
  ))

```

The script includes a comment that reads: "Need to remove ptpts 62938_W and 83249_W who are both double completions" but there is no data from these participants in the folder (any more). We assume that they have already been removed from the dataset uploaded on the OSF:

```{r, results='hide'}
#| label: original code lines 31-46

#####
# Process worker ids
ids = raw_data %>% 
  dplyr::filter(test_part == "worker_id" ) %>%
  mutate(responses = gsub('{\"Q0\":"','',
                          x=responses
                          ,fixed=T),
         responses = gsub('"}','',
                          x=responses
                          ,fixed=T))

summary(as.factor(ids$responses)) # two participants completed twice for some reason
# Need to remove ptpts 62938_W and 83249_W who are both double completions (we keep their first completion)

write_csv(data.frame(cbind(ids$id,ids$responses)), file = "ids.csv")

```

```{r}
#| label: original code lines 48-57

#####
# Process catch questions

catch = test %>% # Read in data
    dplyr::filter(verb %in% c("chase", "drive", "teach", "remind", "carry", "pose", "feed", "hire")) %>%
    mutate(correct = case_when(
      verb == "drive" & responses > 0 ~ 1,
      verb != "drive" & responses < 0 ~ 1,
      TRUE ~ 0
    ))

```

We added code to calculate the average number of correct trials for each id in the "catch" dataset, in order to check how each participant (id) performed:

```{r}
#| label: additional code to check participants' correctness scores

catch |> 
  group_by(id) |>  
  dplyr::summarise(correct = mean(correct)) |> 
  View()

```

In the authors' original R script, 19 participants who failed **2 or more** catch trials are excluded. This differs from the pre-registration (<https://aspredicted.org/7698v.pdf>), which specified excluding participants who answered **more than 2** catch trials incorrectly. There were 8 catch trials, so a score of 0.25 corresponds to 2 out of 8 incorrect trials. Consequently, according to the following code, participants with 2 or more incorrect catch trials (including 3 who got all catch trials wrong) were excluded, resulting in a total of 19 participants excluded. The comment added by the original authors "Exclude 56517_W based on catch trials" is not relevant:

```{r, message=FALSE}
#| label: original code lines 59-81

catch_ids = catch %>% 
  group_by(id) %>% 
  dplyr::summarise(correct = mean(correct)) %>% 
  filter(correct < 0.85)

# Exclude 56517_W based on catch trials

##### reproduction authors: the following code excludes the 19 participants (based on catch trials ids) and calculates participants' response means (summarise) -> = empathy pilot results
empathy_pilot_results = test %>%
  filter(!id  %in% catch_ids$id) %>%
  group_by(id, condition) %>%
  dplyr::summarise(empathy_with_first_mentioned = mean(responses)) %>%
  group_by(condition) %>%
  dplyr::summarise(empathy_with_first_mentioned.m = mean(empathy_with_first_mentioned),
                   empathy_with_first_mentioned.sd = sd(empathy_with_first_mentioned),
                   OverallLikeMe.lo = ci.low(empathy_with_first_mentioned),
                   OverallLikeMe.hi = ci.high(empathy_with_first_mentioned)) %>%
  filter(condition != "catch") %>%
  rename(syntax_unique = condition,
        OverallLikeMe.m = empathy_with_first_mentioned.m) %>%
  mutate(data_type = "3. Empathy Intuitions",
         Participant_Background = "English speakers")

```

We commented the `plot_grid()` code out as it does not work from this script because `LikeMe_score` is not defined:

```{r, results='hide'}
#| label: reproduction of code lines 83-101 to cpmment out plot_grid() code

empathy_score_pilot  = ggplot(data = empathy_pilot_results,
                              aes(x = syntax_unique, y = OverallLikeMe.m, group = data_type)) + 
  #geom_hline(yintercept = 0.5,lty =2)+
  geom_line(color = "black")+
  geom_point(size = 3, color = "black") +
  geom_errorbar(aes(ymin= OverallLikeMe.lo,ymax = OverallLikeMe.hi), width = 0) +
  facet_grid(Participant_Background ~ data_type, scales = "free")+
  theme_cowplot()+ylim(c(-0.5,2)) + geom_hline(yintercept = 0, lty =2 )+
  xlab("")+ylab("Relative Empathy for \nfirst mentioned character") +
  theme(legend.position="bottom", 
        strip.background.y = element_blank(),
        strip.text.y = element_blank()
  )

# plot_grid(LikeMe_score,agency_score, empathy_score_pilot,
#           nrow = 3, labels = "AUTO")  

summary(lmer(responses ~ condition + (1+condition|id), data = test %>%
               filter(!id  %in% c("./pilot_testing/56517_W.csv", "./pilot_testing/62938_W.csv", "./pilot_testing/83249_W.csv") & condition != "catch")))

```

The preprocessing script filters participants but does not export the resulting dataset. Consequently, it was unclear to us whether the data used in the analysis script (Data Analysis/empathy_study_data.csv) matches the output of the preprocessing steps. We therefore wrote additional code to reconstruct the data frame that the authors used in their analysis:

```{r, message=FALSE}
#| label: additional code to reconstruct data frame

write.csv(test, file = "R_scripts/scripts_reproduction/Data_Preprocessing_reproduction/reproduced_data/empathy_study/empathy_data_test.csv", row.names = FALSE)

empathy_study_data_original <- read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "empathy_study_data.csv")) #This is the data used by the authors in their analysis (in the analysis script R_scripts/scripts_and_data_original/Data_Analysis_original/OSF_Analyses.r)

length(unique(test$id)) #128 participants
length(unique(empathy_study_data_original$id)) #109 participants

test_ids <- test |> distinct(id)
original_ids <- empathy_study_data_original |> distinct(id)

reconstructed_df <- test |> 
  filter(!id  %in% catch_ids$id)

supposed_ids <- reconstructed_df |> distinct(id)

write_csv(reconstructed_df, file = "R_scripts/scripts_reproduction/Data_Preprocessing_reproduction/reproduced_data/empathy_study/reconstructed_df.csv")
```

Result: We successfully recreated the dataframe that the authors used in the analysis. However, this procedure confirmed that the data used in the analysis were the data from the original 128 participant minus the 19 that the authors excluded due to catch trials. Therefore, no other exclusion criteria mentioned in the preregistration appear to have been applied by the authors. The preregistration stated that trials with response times more than 3 SD from the mean, participants whose self-reported gender did not match Prolific records, and participants who had reported not to have lived in the UK for the last five years would be excluded. While these additional exclusion criteria might not have been relevant, the shared preprocessing code of this rating study does not check for them.
