---
title: "process_data_reproduction"
format: html
editor: visual
---

```{r}
# From Mike Frank
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)} #  mean(x,na.rm=na.rm) -
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) } #-

```

We added code for library imports for the libraries needed to run the original script. Additionally, we used the library "here" for importing the data to ensure that our R project has robust relative file paths:

```{r, message=FALSE}

library(dplyr)
#GR:added library imports (libraries needed to run the original script + library "here"):
library(lme4)
library(readr)
library(ggplot2)
library(cowplot)
library(here)

#GR: adjusted import code to import data via "here": 
files <- list.files(path = here("R_scripts/scripts_and_data_original/Data_Preprocessing_original/EmpathyStudy/full_empathy_data"), pattern = "\\.csv$", full.names = TRUE)
raw_data <- sapply(files, read_csv, simplify=FALSE) %>% 
  bind_rows(.id = "id")

```

The raw data the authors provided are already anonymised:

```{r}

test = raw_data %>% # Read in data
  dplyr::filter(trial_type == "survey-likert-extra-labels" )%>%
  mutate(responses = gsub('{\"Q0\":','',
                          x=responses
                          ,fixed=T),
         responses = gsub('}','',
                          x=responses
                          ,fixed=T),
         responses = as.numeric(responses)-3,
         responses = ifelse(is.na(name_order), responses, ifelse(name_order == "right_to_left", responses,-1 *responses))
                            ) %>%
  mutate(condition = case_when(
    grepl("_active",verb, fixed = TRUE) ~ "active",
    grepl("_passive",verb, fixed = TRUE) ~ "passive",
    grepl("_conjoined",verb, fixed = TRUE) ~ "conjoined",
    TRUE ~ "catch"
  ))

```

There is a comment "Need to remove ptpts 62938_W and 83249_W who are both double completions" but there is no data from these participants in the folder (anymore). We suppose they have already been removed.

```{r, results='hide'}

#####
# Process worker ids
ids = raw_data %>% 
  dplyr::filter(test_part == "worker_id" ) %>%
  mutate(responses = gsub('{\"Q0\":"','',
                          x=responses
                          ,fixed=T),
         responses = gsub('"}','',
                          x=responses
                          ,fixed=T))

summary(as.factor(ids$responses)) # two participants completed twice for some reason
# Need to remove ptpts 62938_W and 83249_W who are both double completions (we keep their first completion)
#GR: they are already removed from data folder 

write_csv(data.frame(cbind(ids$id,ids$responses)), file = "ids.csv")

```

```{r}

#####
# Process catch questions

catch = test %>% # Read in data
    dplyr::filter(verb %in% c("chase", "drive", "teach", "remind", "carry", "pose", "feed", "hire")) %>%
    mutate(correct = case_when(
      verb == "drive" & responses > 0 ~ 1,
      verb != "drive" & responses < 0 ~ 1,
      TRUE ~ 0
    ))

# ELF: As far as I can see 3 participants got all catch trials wrong
catch %>% 
  group_by(id) %>% 
  dplyr::summarise(correct = mean(correct)) |> 
  View()

```

19 participants who failed **2 or more** catch trials are excluded (this differs from the pre-registration (<https://aspredicted.org/7698v.pdf>), which specified excluding participants who answered **more than 2** catch trials incorrectly):

```{r, message=FALSE}

catch_ids = catch %>% 
  group_by(id) %>% 
  dplyr::summarise(correct = mean(correct)) %>% 
  filter(correct < 0.85) #GR -> 8 catch trials, 0.25= 2/8 (2 out of eight), so they excluded participants with 2 OR MORE (not more than two) incorrect catch trials -> 19 participants (including the 3 who answered all catch trials wrong)

# Exclude 56517_W based on catch trials #GR: this comment is apparently not relevant

#GR: the following code excludes the 19 participants (based on catch trials ids) and calculates participants' response means (summarize) -> = empathy pilot results
empathy_pilot_results = test %>%
  filter(!id  %in% catch_ids$id) %>%
  group_by(id, condition) %>%
  dplyr::summarise(empathy_with_first_mentioned = mean(responses)) %>%
  group_by(condition) %>%
  dplyr::summarise(empathy_with_first_mentioned.m = mean(empathy_with_first_mentioned),
                   empathy_with_first_mentioned.sd = sd(empathy_with_first_mentioned),
                   OverallLikeMe.lo = ci.low(empathy_with_first_mentioned),
                   OverallLikeMe.hi = ci.high(empathy_with_first_mentioned)) %>%
  filter(condition != "catch") %>%
  rename(syntax_unique = condition,
        OverallLikeMe.m = empathy_with_first_mentioned.m) %>%
  mutate(data_type = "3. Empathy Intuitions",
         Participant_Background = "English speakers")

```

```{r, results='hide'}

empathy_score_pilot  = ggplot(data = empathy_pilot_results,
                              aes(x = syntax_unique, y = OverallLikeMe.m, group = data_type)) + 
  #geom_hline(yintercept = 0.5,lty =2)+
  geom_line(color = "black")+
  geom_point(size = 3, color = "black") +
  geom_errorbar(aes(ymin= OverallLikeMe.lo,ymax = OverallLikeMe.hi), width = 0) +
  facet_grid(Participant_Background ~ data_type, scales = "free")+
  theme_cowplot()+ylim(c(-0.5,2)) + geom_hline(yintercept = 0, lty =2 )+
  xlab("")+ylab("Relative Empathy for \nfirst mentioned character") +
  theme(legend.position="bottom", 
        strip.background.y = element_blank(),
        strip.text.y = element_blank()
  )

#GR: Commented this code out, it does not work from this script, as LikeMe_score is not defined:
# plot_grid(LikeMe_score,agency_score, empathy_score_pilot,
#           nrow = 3, labels = "AUTO")  

summary(lmer(responses ~ condition + (1+condition|id), data = test %>%
               filter(!id  %in% c("./pilot_testing/56517_W.csv", "./pilot_testing/62938_W.csv", "./pilot_testing/83249_W.csv") & condition != "catch")))

```

The preprocessing script filters participants but does not export the resulting dataset. Consequently, it was unclear to us whether the data used in the analysis script (Data Analysis/empathy_study_data.csv) matches the output of the preprocessing steps. We therefore added code to reconstruct the data frame the authors used in their analysis:

```{r, message=FALSE}

#GR: added data reproduction code:
write.csv(test, file = "R_scripts/scripts_reproduction/Data_Preprocessing_reproduction/reproduced_data/empathy_study/empathy_data_test.csv", row.names = FALSE)
empathy_study_data_original <- read_csv(here("R_scripts", "scripts_and_data_original", "Data_Analysis_original", "empathy_study_data.csv")) #GR: this is the data used by the authors in their analysis (in the analysis script R_scripts/scripts_and_data_original/Data_Analysis_original/OSF_Analyses.r)

length(unique(test$id)) #128 participants
length(unique(empathy_study_data_original$id)) #109 participants

test_ids <- test |> distinct(id)
original_ids <- empathy_study_data_original |> distinct(id)

reconstructed_df <- test |> 
  filter(!id  %in% catch_ids$id)
supposed_ids <- reconstructed_df |> distinct(id)

write_csv(reconstructed_df, file = "R_scripts/scripts_reproduction/Data_Preprocessing_reproduction/reproduced_data/empathy_study/reconstructed_df.csv")

```

Result: We successfully recreated the dataframe the authors used in the analysis. However, this procedure confirmed that the data used in the analysis were the data from the original 128 participant minus the 19 they excluded due to catch trials. Therefore, no other exclusion criteria mentioned in the preregistration appear to have been applied by the authors. The preregistration stated that trials with response times more than 3 SD from the mean, participants whose self-reported gender did not match Prolific records, and participants who had reported not to have lived in the UK for the last five years would be excluded. While these additional exclusion criteria might not have been relevant, the preprocessing code of this rating study does not check for them.
