---
title: "Process_Chinese_Data_reproduction"
date: last-modified
freeze: true
cache: true
format:
  html:
    embed-resources: true
    number-sections: true
    toc: true
---

```{r}
#| label: original code lines 1-42


######
# Script for processing of raw Chinese data

# Load packages
library(magick)
library(cowplot)
library(tidyr)
library(dplyr)
library(hms)
library(readr)
library(stringr)
library(ggplot2)
library(reshape2)
library(rjson)
library(jsonlite)
library(Matrix)
library(lme4)
library(psych)
library(lmtest)
library(sjPlot)
library(wesanderson)
library(knitr)
library(rmarkdown)
library(MuMIn)
library(pwr)
library(scales)


# From Mike Frank
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)} #  mean(x,na.rm=na.rm) -
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap::bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) } #-


####
# Import and tidy data
files <- list.files(path = "./data_edited_for_spelling", pattern = "*.csv", full.names = T)
raw_data <- sapply(files, read_csv, simplify=FALSE,col_types = cols(.default = "?", ptptID = "c")) %>% 
  bind_rows(.id = "id") %>%
  dplyr::mutate(ppt_race = "asian",) # as all ppts are asian in this study, just in case of coding error


```

we used the {here} library for importing the data to ensure that our R project has robust relative file paths:

```{r}
#| label: reproduction code lines 1-42
library(here)

# Import and tidy data:

files <- list.files(
  here("R_scripts", "scripts_and_data_original", "Data_Preprocessing_original", "Chinese_Study", "data_edited_for_spelling"),
  pattern = "*.csv", full.names = T)


raw_data <- sapply(files, read_csv, simplify=FALSE,col_types = cols(.default = "?", ptptID = "c")) %>% 
  bind_rows(.id = "id") %>%
  dplyr::mutate(ppt_race = "asian",) # as all ppts are asian in this study, just in case of coding error


```

```{r}
#| label: original code lines 43-55


# correct coding error
raw_data[raw_data$subject == 35039,]$ppt_language = "chinese"

stimuli = read_csv(here("R_scripts","scripts_and_data_original", "Data_Preprocessing_original", "Chinese_Study", "gif_stimuli.csv")) %>%
  mutate(list = tolower(list),
         left_name = tolower(left_name),
         right_name = tolower(right_name),
         left_race = tolower(left_race),
         right_race = tolower(right_race),
         left_gender = tolower(left_gender),
         right_gender = tolower(right_gender),
         gif = substr(gif,1,nchar(gif) - 4))
```

```{r}
#| label: original code lines 56-365

test = raw_data %>% # Read in data
  dplyr::select(subject,rt,list,button_pressed,trial_type,trial_index,responses,image,verb,phrase,condition,ppt_language,ppt_gender,ppt_race,test_part) %>%
  dplyr::filter(trial_type == "survey-text" & !test_part %in% c("fiveyears", "worker_id", "demographics")) %>% #Select rows we want
  mutate(gif = gsub('<img src=\'gifs/','',
                    x=image
                    ,fixed=T),
         gif = gsub('.gif\' style=\'height:400px;\'\'></img>','',
                    x=gif
                    ,fixed=T),
         responses = gsub('{\"Q0\":\"','', # Find and replace the nasty characters we don't need
                          x=responses
                          ,fixed=T),
         responses = gsub('{\"q0\":\"','', # Find and replace the nasty characters we don't need
                          x=responses
                          ,fixed=T),
         responses = gsub('\"}','',
                          x=responses
                          ,fixed=T),
         responses = tolower(responses),
         list = tolower(list)) 

test = test %>% #make all responses lower case) 
  left_join(stimuli, by = c("list","condition"="language","gif")) %>% #join the data to the tagged database linking picture name to demog. characteristics
  rowwise() 


test = test %>%
  mutate(left_figure_mentioned = str_detect(responses,left_name), 
         right_figure_mentioned = str_detect(responses,right_name), #search if the left or right figure is in response
         both_figures_mentioned = ifelse(left_figure_mentioned == TRUE & right_figure_mentioned ==TRUE,
                                         TRUE,FALSE), #TRUE if ppts have used both correct names
         first_figure = ifelse(both_figures_mentioned == FALSE, "cannot auto compute", 
                               ifelse(
                                 unlist(gregexpr(pattern =left_name,responses)) < unlist(gregexpr(pattern =right_name,responses)),
                                 "left_name","right_name")), #if left figure is named earlier in string response, then they're mentioned first etc
         first_figure_gender = ifelse(both_figures_mentioned == FALSE,"cannot auto compute", #add columns for gender and race of the first mentioned person
                                      ifelse(first_figure == "left_name",left_gender,right_gender)),
         first_figure_race = ifelse(both_figures_mentioned == FALSE,"cannot auto compute", #add columns for gender and race of the first mentioned person
                                    ifelse(first_figure == "left_name",left_race,right_race)),
         syntax_correct = str_detect(responses,phrase),
         excluded_trial_mention = ifelse(both_figures_mentioned == FALSE,"excluded","included"),
         excluded_trial_syntax = ifelse(syntax_correct == FALSE,"excluded","included"),
         excluded_trial = ifelse(excluded_trial_mention == "included" & excluded_trial_syntax == "included","included","excluded")
  ) 



#create new columns for man_first to analyse overall trends later

test$man_first <- ifelse(test$first_figure_gender == "male", 1, 
                         ifelse(test$first_figure_gender == "female",0,NA)) #create numerical column
test$asian_first <- ifelse(test$first_figure_race == "asian", 1, 
                           ifelse(test$first_figure_race == "black",0,NA)) #create numerical column


#Create df to check descriptives
descriptives_data <- subset(raw_data, test_part == "demographics" & trial_type=="survey-text")
#CHECK LISTS
table(descriptives_data$list,descriptives_data$ppt_gender, descriptives_data$ppt_language)
#equal number of participants in all lists across demographic conditions


#create new trial order column called trial_number, 1 - 80 for each ppt

test$trial_number <- rep(1:90, length=nrow(test))


#Checking worker IDs for missing data

worker_id = raw_data %>% # Read in data
  dplyr::filter(test_part %in% c("worker_id"))%>%
  dplyr::select(subject,responses,test_part)%>%
  mutate(responses = gsub('{\"Q0\":\"','', # Find and replace the nasty characters we don't need
                          x=responses
                          ,fixed=T))%>%
  mutate(responses = gsub('\"}','',
                          x=responses
                          ,fixed=T))

#####
# Participant exclusions

data_bad <- subset(test, excluded_trial == "excluded", na.rm = T) #df for all bad trials. Use to clean data

#write_csv(data_bad,"bad_trials.csv")

write_csv(data_bad, here("R_scripts/scripts_reproduction/Data_Preprocessing_reproduction/reproduced_data/chinese_study/bad_trials.csv"))

#M: added path to reproduced_data

verbal_exclusions = data_bad %>%
  dplyr::group_by(subject,list,condition,ppt_race,ppt_gender) %>%
  dplyr::summarise(n_excl = length(excluded_trial)) %>% #count number of excluded trials
  dplyr::filter(n_excl > 32) #filter out trials on which ppt got it wrong on over 50% of trials
verbal_exclusions


newdata <- subset(test, !subject %in% verbal_exclusions$subject) #remove 6 entire subjects who fell below threshold for inclusion (must have at least 40 valid trials (50%))

newdata <- subset(newdata, excluded_trial!="excluded") #remove individual invalid responses (invalid trials)

#####
# Exclude for orientation bias

test$left_bias <- ifelse(test$first_figure == "left_name", 1, 0) # Was left figure mentioned first? This will be used to determine if >90% of ptpts trials had a left bias
test$right_bias <- ifelse(test$first_figure == "right_name",1,0) # Measure right figure mentioned first? This will be used to determine if >90% of ppts trials had a right bias


#overall means by list, ppt gender, ppt race  etc
data_summary <- test %>%
  dplyr::select(subject,list,trial_type,responses,left_bias,right_bias,ppt_gender,excluded_trial) %>%
  dplyr::group_by(subject,ppt_gender,list) %>%
  dplyr::summarize(left_bias.subj.mean = mean(left_bias,na.rm=T), # get ppt mean left bias
                   right_bias.subj.mean = mean(right_bias,na.rm=T)) %>% # get ppt mean right bias bias
  dplyr::mutate(orientation_bias.subj.mean = ifelse(left_bias.subj.mean >= right_bias.subj.mean, # Create column that shows overall orientation bias (i.e., the larger of the left/right biases)
                                                    left_bias.subj.mean, right_bias.subj.mean)) %>%
  dplyr::group_by(list,ppt_gender) %>%
  dplyr::summarise(orientation_bias.mean = mean(orientation_bias.subj.mean,na.rm=T), #Summarise orientation bias by list etc
                   orientation_bias.sd = sd(orientation_bias.subj.mean))

#overall means averaging across all ppts
test %>%
  dplyr::select(subject,list,trial_type,responses,left_bias,right_bias,ppt_gender,condition,excluded_trial) %>%
  dplyr::group_by(subject,ppt_gender,condition,list) %>%
  dplyr::summarize(left_bias.subj.mean = mean(left_bias,na.rm=T),
                   right_bias.subj.mean = mean(right_bias,na.rm=T)) %>%
  dplyr::mutate(orientation_bias.subj.mean = ifelse(left_bias.subj.mean >= 
                                                      right_bias.subj.mean, left_bias.subj.mean, right_bias.subj.mean)) %>%
  dplyr::group_by(ppt_gender,condition) %>%
  dplyr::summarise(orientation_bias.mean = mean(orientation_bias.subj.mean,na.rm=T),
                   orientation_bias.sd = sd(orientation_bias.subj.mean))

#Overall left bias across all 4 demographic groups is 0.57


#subject means - how are ppts responding, what's their L-R bias?
data_summary2 <- test %>%
  dplyr::select(subject,list,trial_type,responses,image,phrase,left_bias,right_bias,ppt_gender,ppt_race,test_part,excluded_trial,condition) %>%
  dplyr::group_by(subject,ppt_gender,ppt_race,condition,list) %>%
  dplyr::summarize(left_bias.subj.mean = mean(left_bias,na.rm=T), # get ptpt mean left bias
                   right_bias.subj.mean = mean(right_bias,na.rm=T)) %>% # get ptpt mean right bias bias
  dplyr::mutate(orientation_bias.mean = ifelse(left_bias.subj.mean >= right_bias.subj.mean, 
                                               left_bias.subj.mean, right_bias.subj.mean)) # Create column that shows overall orientation bias for each subject (i.e., the larger of the left/right biases)

orientationbias_excluded = data_summary2 %>%
  dplyr::filter(!(orientation_bias.mean >=0.1 & orientation_bias.mean <=0.9))


orientation_bias_plot <- ggplot(data_summary2, aes(x = ppt_gender, y = orientation_bias.mean)) +
  geom_jitter(width = 0.3,height = 0, color="black")+
  geom_hline(yintercept = c(0.9), color = "grey")+
  geom_hline(yintercept = c(0.1), color = "grey")+
  xlab("Participant gender")+
  ylab("Bias to one orientation")+
  theme_minimal()+
  scale_x_discrete(limits = c("man", "woman"),
                   labels = c("Men", "Women"))+
  theme(plot.title = element_text(color="black", size=16, face="bold", hjust = 0.5),
        axis.text.x = element_text(color = "black", size = 16),
        axis.text.y = element_text(color = "black", size = 16),
        axis.title.x = element_text(color="black", size=16, face="bold"),
        axis.title.y = element_text(color="black", size=16, face="bold"))
orientation_bias_plot

#Exclude participants for an orientation bias of over 0.9 (all left bias) and under 0.1 (right bias)
newdata <- subset(newdata, !subject %in% orientationbias_excluded$subject)

#####
# Exclude for slow RTs
#Make rt numeric
newdata$rt <- as.numeric(as.character(newdata$rt), na.rm=T)

rt_average <- newdata %>%
  dplyr::select(subject,rt,list,trial_type,responses,image,phrase,
                ppt_gender,ppt_race,test_part,excluded_trial) %>%
  dplyr::group_by(subject) %>%
  dplyr::summarize(rt.mean = mean(rt,na.rm=T),
                   rt.sd = sd(rt,na.rm=T),
                   rt.se = sd(rt,na.rm=T)/sqrt(length(subject)))

#combine rt_average df with main df

data <- merge(newdata, rt_average, by="subject")


data <- data %>%
  dplyr::filter(!(rt > (rt.mean + (rt.sd * 3))))

data %>% 
  group_by(condition, ppt_gender,list) %>%
  summarise(n = length(unique(subject)))


#####
# Final processing and saving datafile
data$ppt_gender = as.factor(data$ppt_gender)
contrasts(data$ppt_gender)[1] <- -1
data$condition = as.factor(data$condition)
contrasts(data$condition)[1] <- -1
# Make the like me measure
data$ppt_gender_code = ifelse(data$ppt_gender == "man","male","female")
data$LikeMeGender <- ifelse(data$first_figure_gender == data$ppt_gender_code, 1, 0) #create numerical column

data = data %>%
  mutate(OverallLikeMe = ifelse(
    picture_condition %in% c("race_male","race_female"), asian_first,LikeMeGender)
  )

```

```{r}
#| label: original code lines 261-265, TrialType
#| eval: false
#| echo: true

# This is the datafile that we use for our main statistical analyses of this study
write_csv(data,"study5_chinese.csv")
# This is the datafile we join to studies 1-3 for the omnibus analysis
write_csv(data %>% mutate(ppt_demog = ifelse(ppt_gender == "man", "Asian Man","Asian Woman")) %>% left_join(read_csv(here("R_scripts","scripts_and_data_original", "Data_Preprocessing_original", "Chinese_Study","verbs.csv"))) %>% 
            select(subject,english_translation,OverallLikeMe, TrialType, ppt_demog)  %>% rename(event = english_translation) ,"data5_chinese.csv")
```

We get the error message, that the column TrialType does not exist.

```{r}
#| label: reproduction code lines 261-265, trial_type

# This is the datafile that we use for our main statistical analyses of this study
write_csv(data, file = here("R_scripts", "scripts_reproduction", "Data_Preprocessing_reproduction", "reproduced_data", "chinese_study", "study5_chinese.csv"))
# This is the datafile we join to studies 1-3 for the omnibus analysis
write_csv(data %>% mutate(ppt_demog = ifelse(ppt_gender == "man", "Asian Man","Asian Woman")) %>% left_join(read_csv(here("R_scripts","scripts_and_data_original", "Data_Preprocessing_original", "Chinese_Study","verbs.csv"))) %>% 
            select(subject,english_translation,OverallLikeMe, trial_type, ppt_demog)  %>% rename(event = english_translation), here("R_scripts", "scripts_reproduction" ,"Data_Preprocessing_reproduction", "reproduced_data", "chinese_study", "data5_chinese.csv"))
```

Note: the command `write_csv()` does not work because of the following error: "Error in `select()`: ! Can't select columns that don't exist.✖ Column `TrialType` doesn't exist. Run `rlang::last_trace()` to see where the error occurred." By changing `TrialType` to `trial_type` it is possible to save a new csv-file, but the column in this dataset only contains the observation "survey-text".
